I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-27 Paper/experiments.tex
edits

\begin{table}[htb]
	\centering

		\begin{tabularx}{0.9\textwidth}{|C||C|C|C|C|C|}

		\hline
		\text{DNN} & \shortstack{DeepPoly/\\CROWN} & PRIMA & $\beta$-CROWN & {\toolname} & \shortstack{Upper\\Bound}\\ 
		\hline \hline

		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & {$68.4\%$} &  $84.2 \%$ \\ 
		$\epsilon = 0.026$ & 5s & 159s & 102s & {142s} &  \\
		\hline

		$5 \times 200$ \  &  $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & {$76.8\%$} & 
		$90.1 \%$\\ 
		$\epsilon = 0.015$ & 11s & 224s & 86s & {279s}  &\\ \hline \hline

		$8\times100$\  &   $29.2\%$ & $42.8\%$ & $62\%$ & {$\mathbf{65.8\%}$}  & $82.0 \%$ \\ 
		$\epsilon = 0.026$ & 8s & 301s & 103s & {346s} & \\
		\hline

		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & {$\mathbf{80.7\%}$} & $91.1 \%$ \\ 
		$\epsilon = 0.015$ & 17s & 395s & 95s  & {697s$^\star$} & \\ \hline

		%6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time & \\ 
		%$\epsilon = 0.035$ & & & & & & & & & &\\ \hline
	\end{tabularx}

	\caption{$\%$ of verified images and average runtime in seconds, over 1000 images. 
		Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.
%		\newline $^\star$ For $8 \times 200$, slow fixed results are obtained after running slow adaptative.
}
	\label{tab:example}
\end{table}

@@

For DNNs robustly trained, $\alpha$-$\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close \cite{crown} to the upper bound on the $\%$ of verified images \cite{attack}. Compensation strength is not required in these contexts, reason why we did not consider it.

>>>>

\begin{table}[htb]
	\centering
	\begin{tabularx}{\textwidth}{|C||C|C|C|C|C|}

		\hline
		\text{DNN} & \shortstack{Upper\\Bound} & \shortstack{DeepPoly/\\CROWN} & PRIMA & $\beta$-CROWN & {\toolname}\\ 
		\hline \hline

		$5 \times100$\  & $84.2 \%$ & $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & {$68.4\%$}\\ 
		$\epsilon = 0.026$ &  & 5s & 159s & 102s & {142s}\\
		\hline

		$5 \times 200$ \  & $90.1 \%$ & $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & {$76.8\%$}\\ 
		$\epsilon = 0.015$ &  & 11s & 224s & 86s & {279s} \\ \hline \hline

		$8\times100$\  & $82.0 \%$ & $29.2\%$ & $42.8\%$ & $62\%$ & {$\mathbf{65.8\%}$}\\ 
		$\epsilon = 0.026$ &  & 8s & 301s & 103s & {346s}\\
		\hline

		$8\times200$\  & $91.1 \%$ & $25.9\%$ & $62.4\%$ & $73.5\%$ & {$\mathbf{80.7\%}$}\\ 
		$\epsilon = 0.015$ &  & 17s & 395s & 95s  & {697s$^\star$}\\ \hline

		$6\times500$\  & $92\%$ & $26\%$ & $32.5\%$ & $41\%$ & 65\%\\ 
		$\epsilon = 0.035$ &  & 34s & 119s & 18.4s & 925s\\ \hline

	\end{tabularx}

	\caption{$\%$ of verified images and average runtime in seconds.
		Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.
	}
	\label{tab:example}
\end{table}

@@

Our focus in this study was solely on DNNs employing ReLU activation functions since our approached on usage of MILP, which is naturally suited for ReLU activation function. That said, it is worth remarking that the notion of compensation strength is independent of

The rationale lies in the capability of MILP, the foundational component of {\toolname} (and branch-and-bound in the context of $\beta$-CROWN), to efficiently handle ReLU activations.

While other activation functions can be abstracted, as seen with PRIMA (contrary to $\beta$-CROWN), the concept of compensation remains independent of the activation function used. We leave studying the

We acknowledge the potential value in exploring compensation strength across varied activation functions and earmark this for subsequent research.
